### 2015-11-11 AssignmentV/Assignment5-Ditz_Schroeder-WS15-16.tex
nicht viel passiert nur die überschriften hinzugefügt
erster lösungsvorschlag für aufgabe 1

\section*{Theoretical Assignment - \textsl{Optimal multiple alignment}}

\newpage
\bibliography{Assignment4-Ditz_Schroeder-WS15-16.bib}
\bibliographystyle{ieeetr}

>>>>

\section*{Theoretical Assignment - \textsl{Comparison with at most $l$ mismatches}}

Assume two sequences of length t with l mismatches. In the worst case, all mismatches are 
distributed uniformly. Than both sequences will share $l+1$ tuples of length $\lfloor\frac{t}{l+1}\rfloor$.\\
\\
\noindent So both sequences share $l+1$ k-tuples of length $k = \lfloor\frac{t}{l+1}\rfloor$ and for each 
$k \le \lfloor\frac{t}{l+1}\rfloor$ they share $l+1 * \lfloor\frac{\lfloor\frac{t}{l+1}\rfloor}{k}\rfloor$
k-tuples.

\section*{Theoretical Assignment - \textsl{Linear programming by hand}}

\section*{Theoretical Assignment - \textsl{Bonus: Carillo-Lipman bound}}

%\newpage
%\bibliography{Assignment4-Ditz_Schroeder-WS15-16.bib}
%\bibliographystyle{ieeetr}
